DATA 624 Homework 4

### 2020-03-01 DATA624/HW4.Rmd
More work on HW4

**Before looking at the relationships I think it would be helpful to know a bit more about the predictors.  T element concentrations predictors' unit of measurement, according to [UCI documentation](http://archive.ics.uci.edu/ml/datasets/Glass+Identification) is the "weight percent in corresponding oxide."  There is no documentation on the refractive index provided by UCI.  But according to Wikipedia, the refractive index measure how much light slows down by passing through a material.  An increasing refractive index corresponds to decreasing speed of light in the material.**

**Now that we have an inkling of what the data represent, we will take a look at the distribution of the predictors:**

@@

**Now we will examine how the predictors are related to eachother.  We will do that with a correlation plot.**

@@

**I am assuming the degenerate distibuted variaviables discussed earlier in the chapter referes to section 3.5 on removing predictors.  Here's some frequency tables:**

@@

**If one of the important variables has a lot of missing data I would use k-means to fill in the holes with this categorical data.  If the variables were quantitative I would probably use the mean or median to fill in the holes.**

>>>>

**First we will take a look at the distribution of the predictors:**

@@

**Now we will examine how the predictors are related to each other.  We will do that with a correlation plot.**

@@

**I am assuming the degenerate distibuted variaviables discussed earlier in the chapter refers to section 3.5 on removing predictors.  Here's some frequency tables:**

@@

**If one of the important variables has a lot of missing data I would use knn to fill in the holes with this categorical data.  If the variables were quantitative I would probably use the mean or median or k-means to fill in those holes.**
